%text.tex

\documentclass{article}
\usepackage{times}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{url}
\usepackage{amssymb}
\DeclareGraphicsExtensions{.pdf}
\title{CSE881 - Project Proposal}
\author{Sorrachai Yingchareonthawornchai, Vaibhav Sharma \\
 \texttt{yingchar@msu.edu}, \texttt{sharmav6@msu.edu}\\
}
\begin{document}
\maketitle
\section{Fraudulent Resume Detection}
\textbf{Project type:} Prototype Development
\\
\textbf{Problem statement:} given a resume, determine whether or not the resume
is fabricated. \\
\textbf{Goal:} return a value for a given resume with links or evidences to
original resume in database. \\

We define a resume as a set of sections. A section contains a collection of
sentences. We assume that the document has XML format. We regard
techniques in natural language processing as not in scope of this
project. The problem statement of this project is also requested as a solution by a company which will be providing us with the data needed for this project.\\

\textbf{Overview of tasks}\\
In the preprocessing step, we create a document parser that takes in
resumes as input. While the format of the resumes is undecided as of now, we are looking if the XML format of the resumes can be used to shorten the preprocessing step. The output is a set of sections containing
topics and its sentences.  The next step is to identify indicators
that we need to perform detection. The challenges in extracting such indicators will range from simple to difficult. For example, one simple indicator would be matching
university name in the Education Section with our fake university list. Another example would be checking consistency
regarding description of the company against company name (e.g.,
``Company Name: Meijer, Description: a nuclear power plant design company'' does not make
sense). Each indicator could be a data mining task. Once we have
all indicators, we regards them as feature of the document. We then
perform classification to output a degree of fraudulence and
confidence level. Finally, we will build an interactive system that
helps visualize the model and outputs. 

Brief summary of tasks: 
\begin{enumerate}
\item Document parser (Preprocessing)
\item Indication function (Feature extraction)
\item Classification using extracted features
\item An Interactive system that users can interact with
\end{enumerate}
\end{document}
